Tor's Usability for Censorship Circumvention

### 2016-04-05 pets2017-paper/pets2017-paper.tex
rename weird results subsubsubsection
future work section

\subsubsection{Results}

@@

\section{Future Work} 
{\color {red}
Wait to fill this section out until we have finished analyzing the data from the quantitative
user study experiment. OR, maybe this section isn't even necessary.\\

\noindent {\bfseries Changing the Current Interface} merge, push. \\

\noindent{\bfseries Finishing Touches} 
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
\item {\bfseries Detecting the need for proxies.} We hacked this together for now. 
\item {\bfseries Handling rare error cases.} Mention clock drift and proxy connection cases.
\item {\bfseries Additional user feedback.} Animation in the progress window. 
\item {\bfseries Stylization.} Comply with design style guides, if any. 
\end{itemize}

\noindent{\bfseries Measuring Impact} Tor metrics to see if this is helping at the large scale, and for future user study work in general. 
}

>>>>

\subsubsection{Changes During the Experiment}

@@

\section{Future Work} 
Throughout the qualitative user study, redesign of the interface, and the quantitative user study, we collaborated and communicated with Tor developers. Redesigning the configuration interface was a mutual interest. In fact, Tor version {\color{red} 5.?.?} incorporated textual and navigational changes based on our redesigned interface. We plan to continue our work with Tor developers to integrate changes we found to be helpful. This process will entail debugging our code, merging changes with the current version of Tor, making high-fidelity graphics that align with style guides, and finalizing the advice to give to users in the interface.

Ideally, we want users in censorship environments across the world to succeed in connecting to the Tor network in a couple of minutes. Currently, the deployed nor redesigned interface achieves this goal. Additional user studies that focus specifically on users in heavily censored environments, or increasing the amount of automation in the configuration process can yield to higher rates of success and faster time to success. We encourage future work to explore some of the non-conservative changes and alternative approaches that we were not able to test in these series of experiment, which are listed in Section \ref{sec:discussion}.
